Distributional Trees and Forests

### 2017-11-09 pkg/disttree/inst/draft/draft.Rnw
edited plots
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1689 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: c648d42d2eccbc7bc58393b5abcb0904ab23579b

%% packages
\usepackage{amstext}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{thumbpdf}
\usepackage{rotating}
\usepackage{caption}
\captionsetup{format=hang}
\usepackage{subcaption}
\usepackage{Sweave}
\usepackage{enumitem}
\usepackage{array, makecell}
\usepackage{tikz}
\usetikzlibrary{positioning,shapes,arrows,decorations.pathreplacing,calc,automata,mindmap}
%\usepackage[pagebackref=true]{hyperref}
%\usepackage{doi}

@@

#legendheight
lh1 <- crch::dcnorm(0.01, mean = df_mu[1], sd = df_sigma[1], left = 0)
lh2 <- crch::dcnorm(0.01, mean = df_mu[2], sd = df_sigma[2], left = 0)
lh3 <- crch::dcnorm(0.01, mean = df_mu[3], sd = df_sigma[3], left = 0)
@

@@

\SweaveOpts{eval = FALSE}

<<echo=FALSE, results=hide>>=
source("oneset.R")
if(file.exists("oneset1.rda")){
  load("oneset1.rda")
} else {

  library("gamlss.cens")
  gen.cens("NO", type = "left")

  kappa <- 1
  fun <- function(x){
    mu <- 0.2 + 
      (10 * (exp(-(3*x[,1]-1.2)^(2*kappa)))) * as.numeric(x[,1] < 0.4) + 
      (10 * (exp(-(3*x[,1]-1.2)^(2*kappa))) * (1/2) + 10/2) * as.numeric(x[,1]>= 0.4) #+
    #(3 * (exp(-(3*x[,1]-1.2)^(2*kappa)))) +
    #(3 * (exp(-(3*x[,1]-1.2)^(2*kappa)))) * x[,4]
    sigma <- 0.5 + 
      #mu/5 + 
      2 * (x[,1] < -0.4) + 
      3 * x[,4] #+
    #1*(x[,1] < -0.7) 
    #plogis((kappa^(1.8)) * 4 * (x[,2] + 0.7)) #* x[,4]
    #4*(1-plogis((kappa^(1.8)) * 2 * (x[,1] + 0.5))) * x[,4]
    #5 * abs(x[,1]) * x[,4]
    par <- cbind(mu, sigma)
    return(par)
  }

  oneset1 <- sim_oneset(parfun = fun, nobs = 500, seedconst = 74, ntree = 100,
                        formula = y~x1+x2+x3+x4+x5+x6, 
                        #formula = y~x1+x2+x4+x5,
                        #formula = y~x1+x2+x3,
                        tree_minsplit = 20, tree_minbucket = 7, tree_mincrit = 0.95, 
                        forest_minsplit = 20, forest_minbucket = 7, forest_mincrit = 0, 
                        forest_mtry = 3, type.tree = "ctree", 
                        censNO = TRUE, 
                        pred_fix = TRUE,
                        pred_fix_x1 = 0.9,
                        pred_fix_x2 = 0.9,
                        pred_fix_x4 = 1,
                        gamboost_cvr = FALSE,
                        eval_disttree = TRUE,
                        eval_distforest = TRUE,
                        eval_gamlss = TRUE,
                        nrunif = 3,
                        nrcovform = 6)

  save(oneset1, file = "oneset1.rda")
}

if(file.exists("oneset10.rda")){Hans-Brenner-Platz
  load("oneset10.rda")
} else {

  library("gamlss.cens")
  gen.cens("NO", type = "left")

  kappa <- 10
  fun <- function(x){
    mu <- 0.2 + 
      (10 * (exp(-(3*x[,1]-1.2)^(2*kappa)))) * as.numeric(x[,1] < 0.4) + 
      (10 * (exp(-(3*x[,1]-1.2)^(2*kappa))) * (1/2) + 10/2) * as.numeric(x[,1]>= 0.4) #+
    #(3 * (exp(-(3*x[,1]-1.2)^(2*kappa)))) +
    #(3 * (exp(-(3*x[,1]-1.2)^(2*kappa)))) * x[,4]
    sigma <- 0.5 + 
      #mu/5 + 
      2 * (x[,1] < -0.4) + 
      3 * x[,4] #+
    #1*(x[,1] < -0.7) 
    #plogis((kappa^(1.8)) * 4 * (x[,2] + 0.7)) #* x[,4]
    #4*(1-plogis((kappa^(1.8)) * 2 * (x[,1] + 0.5))) * x[,4]
    #5 * abs(x[,1]) * x[,4]
    par <- cbind(mu, sigma)
    return(par)
  }

  oneset10 <- sim_oneset(parfun = fun, nobs = 500, seedconst = 74, ntree = 100,
                        formula = y~x1+x2+x3+x4+x5+x6, 
                        #formula = y~x1+x2+x4+x5,
                        #formula = y~x1+x2+x3,
                        tree_minsplit = 20, tree_minbucket = 7, tree_mincrit = 0.95, 
                        forest_minsplit = 20, forest_minbucket = 7, forest_mincrit = 0, 
                        forest_mtry = 3, type.tree = "ctree", 
                        censNO = TRUE, 
                        pred_fix = TRUE,
                        pred_fix_x1 = 0.9,
                        pred_fix_x2 = 0.9,
                        pred_fix_x4 = 1,
                        gamboost_cvr = FALSE,
                        eval_disttree = TRUE,
                        eval_distforest = TRUE,
                        eval_gamlss = TRUE,
                        nrunif = 3,
                        nrcovform = 6)

  save(oneset10, file = "oneset10.rda")
}
@

\begin{figure}[t!]
\begin{subfigure}{0.6\textwidth}
<<sim_oneset1_mu, fig=TRUE, echo=FALSE>>=
plot_oneset(oneset1, only_dt = FALSE, only_df = FALSE, only_g = FALSE,
              compare_mu = TRUE, 
              add_dt = TRUE,
              add_df = TRUE,
              add_g = TRUE,
              nomodel = FALSE)
@
\end{subfigure}
\hspace{-1cm}
\begin{subfigure}{0.6\textwidth}
<<sim_oneset1_sigma, fig=TRUE, echo=FALSE>>=
  plot_oneset(oneset1, only_dt = FALSE, only_df = FALSE, only_g = FALSE,
              compare_mu = FALSE,
              compare_sigma_line = TRUE, 
              add_dt = TRUE,
              add_df = TRUE,
              add_g = TRUE,
              nomodel = TRUE)
@
\end{subfigure}
\caption{\label{plot_sim_oneset1} ... }
\end{figure}

\begin{figure}[t!]
\begin{subfigure}{0.6\textwidth}
<<sim_oneset10_mu, fig=TRUE, echo=FALSE>>=
plot_oneset(oneset10, only_dt = FALSE, only_df = FALSE, only_g = FALSE,
              compare_mu = TRUE, 
              add_dt = TRUE,
              add_df = TRUE,
              add_g = TRUE,
              nomodel = FALSE)
@
\end{subfigure}
\hspace{-1cm}
\begin{subfigure}{0.6\textwidth}
<<sim_oneset10_sigma, fig=TRUE, echo=FALSE>>=
  plot_oneset(oneset10, only_dt = FALSE, only_df = FALSE, only_g = FALSE,
              compare_mu = FALSE,
              compare_sigma_line = TRUE, 
              add_dt = TRUE,
              add_df = TRUE,
              add_g = TRUE,
              nomodel = TRUE)
@
\end{subfigure}
\caption{\label{plot_sim_oneset10} ... }
\end{figure}

@@

<<pit_qqr, echo=FALSE, eval=TRUE, results=hide>>=

## get predicted parameter
# for learndata and testdata
{

  ## disttree
  if(FALSE){
    # in sample
    pdt <- predict(res$dt, type = "parameter")
    dt_mu_l <- pdt$mu 
    dt_sigma_l <- pdt$sigma 
    pit_dt_l <- cbind(0, pnorm(res$learndata[,"robs"], mean = dt_mu_l, sd = dt_sigma_l))
    pit_dt_l[res$learndata[,"robs"]>0, 1] <- pit_dt_l[res$learndata[,"robs"]>0, 2]
  }  
  # out of sample
  pdt <- predict(res$dt, type = "parameter", newdata = res$testdata)
  dt_mu_t <- pdt$mu 
  dt_sigma_t <- pdt$sigma 
  pit_dt_t <- cbind(0, pnorm(res$testdata[,"robs"], mean = dt_mu_t, sd = dt_sigma_t))
  pit_dt_t[res$testdata[,"robs"]>0, 1] <- pit_dt_t[res$testdata[,"robs"]>0, 2]

>>>>

%% packages
\usepackage{amstext}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{thumbpdf}
\usepackage{rotating}
\usepackage{caption}
\captionsetup{format=hang}
\usepackage{subcaption}
\usepackage{Sweave}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{array, makecell}
\usepackage{tikz}
\usetikzlibrary{positioning,shapes,arrows,decorations.pathreplacing,calc,automata,mindmap}
%\usepackage[pagebackref=true]{hyperref}
%\usepackage{doi}

@@

#legendheight
lh1 <- crch::dcnorm(0.01, mean = df_mu[1], sd = df_sigma[1], left = 0)
lh2 <- crch::dcnorm(0.01, mean = df_mu[2], sd = df_sigma[2], left = 0)
lh3 <- crch::dcnorm(0.01, mean = df_mu[3], sd = df_sigma[3], left = 0)

## get predicted parameter
# for learndata and testdata
{
  ## disttree
  if(FALSE){
    # in sample
    pdt <- predict(res$dt, type = "parameter")
    dt_mu_l <- pdt$mu 
    dt_sigma_l <- pdt$sigma 
    pit_dt_l <- cbind(0, pnorm(res$learndata[,"robs"], mean = dt_mu_l, sd = dt_sigma_l))
    pit_dt_l[res$learndata[,"robs"]>0, 1] <- pit_dt_l[res$learndata[,"robs"]>0, 2]
  }  
  # out of sample
  pdt <- predict(res$dt, type = "parameter", newdata = res$testdata)
  dt_mu_t <- pdt$mu 
  dt_sigma_t <- pdt$sigma 
  pit_dt_t <- cbind(0, pnorm(res$testdata[,"robs"], mean = dt_mu_t, sd = dt_sigma_t))
  pit_dt_t[res$testdata[,"robs"]>0, 1] <- pit_dt_t[res$testdata[,"robs"]>0, 2]

}
@

@@

<<echo=FALSE, results=hide>>=

if(!(file.exists("plot_oneset1_mu.jpeg") & file.exists("plot_oneset1_sigma.jpeg") &
   file.exists("plot_oneset10_mu.jpeg") & file.exists("plot_oneset10_sigma.jpeg"))){

  library("gamlss.cens")
  gen.cens("NO", type = "left")
  source("oneset.R")

\begin{figure}[t!]
\begin{subfigure}{0.6\textwidth}
\includegraphics{plot_oneset1_mu.jpeg}
\end{subfigure}
\hspace{-1cm}
\begin{subfigure}{0.6\textwidth}
\includegraphics{plot_oneset1_sigma.jpeg}
\end{subfigure}
\caption{\label{plot_sim_oneset1} ... }
\end{figure}

\begin{figure}[t!]
\begin{subfigure}{0.6\textwidth}
\includegraphics{plot_oneset10_mu.jpeg}
\end{subfigure}
\hspace{-1cm}
\begin{subfigure}{0.6\textwidth}
\includegraphics{plot_oneset10_sigma.jpeg}
\end{subfigure}
\caption{\label{plot_sim_oneset10} ... }
\end{figure}

@@
